Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-23 CONCUR2018/paper.tex
nudge
+ copyright and subjclass

>>>>

\Copyright{Cattaruzza, David, Abate, Kroening}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Computer systems organization~Embedded software}% mandatory: Please choose ACM 2012 classifications from https://www.acm.org/publications/class-2012 or https://dl.acm.org/ccs/ccs_flat.cfm . E.g., cite as "General and reference $\rightarrow$ General literature" or \ccsdesc[100]{General and reference~General literature}.
